---
output:
  md_document:
    variant: gfm
---

[![Travis-CI Build Status](https://travis-ci.org/vegawidget/vegablock.svg?branch=master)](https://travis-ci.org/vegawidget/vegablock)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/vegablock)](https://cran.r-project.org/package=vegablock)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# vegablock

The goal of vegablock is to provide an interface between Vega and Blocks.

The [Blocks](https://bl.ocks.org) website provides a way to share JavaScript-based visualizations using GitHub gists; the [**vegawidget**](https://vegawidget.github.io/vegawidget) package provides a way to compose and render Vega(-Lite) (JavaScript) visualizations using R. This package provides a bridge between the Blocks website and the vegawidget package. 
  
If you have a GitHub account, you can use this package to deploy Vega(-Lite) blocks. Further, if a block contains a Vega(-Lite) specification and meets a specific format, you can use this package to import such a specification to your R environment.

## Installation

For now, you can install vegablock from GitHub:

```r
# install.package("devtools")
install_github("vegawidget/vegablock")
```

To make things easiest, you should have these environment variables set in your `.Renviron` file:

- `GITHUB_PAT` - a GitHub [Personal Access Token (PAT)](https://github.com/settings/tokens) you create; its scope will have to include *gists*.

- `GITHUB_USERNAME` - your GitHub-account name.

If want to include preview and thumb images with the block, you will need **[nodejs](https://nodejs.org/en/)** installed on your system, and the **[processx](https://processx.r-lib.org/)** and **[magick](https://github.com/ropensci/magick#readme)** packages.

## Examples

```{r message=FALSE}
library("vegablock")
library("vegawidget")
```

With the environment variables set, you can create a block from vegaspec:

```{r eval=FALSE}
vw_create_block(spec_mtcars)
```

```{r echo=FALSE}
message(
  "block url: https://bl.ocks.org/06a512525fbe7a96e1a2028e1871b61c\n",
  " gist url: https://gist.github.com/06a512525fbe7a96e1a2028e1871b61c"
)
```

You can visit the created block [here](https://bl.ocks.org/06a512525fbe7a96e1a2028e1871b61c).

If the block has a specific format, where the Vega(-Lite) specification is in its own file, you can retrieve a vegaspec from a block into your R environment:

```{r}
vw_retrieve_block("06a512525fbe7a96e1a2028e1871b61c")
```
