---
output:
  md_document:
    variant: markdown_github
---

[![Travis-CI Build Status](https://travis-ci.org/<USERNAME>/<REPO>.svg?branch=master)](https://travis-ci.org/<USERNAME>/<REPO>)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/vegablock)](https://cran.r-project.org/package=vegablock)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# vegablock

The goal of vegablock is to provide an interface between Vega and Blocks.

The Blocks website <https://bl.ocks.org> provides a way to share JavaScript-based visualizations; the vegawidget package provides a way to compose and render Vega (JavaScript) visualizations using R. This package provides a bridge between the Blocks website and the vegawidget package. 
  
If you have a GitHub account, you can use this package to deploy Vega(-Lite)blocks. Further, if a block contains a Vega(-Lite) specification and meets a specific format, you can use this package to import such a specification.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```
